crop

### 2023-05-11 scripts/crop2boundary.Rmd
added function for political information

>>>>

```{r modify names of variables to be in proper formats, eval = F}

sf::st_read('../geodata/political/political.shp', quiet = T) %>% 
  rename(County = COUNTY, State = STATE) %>% 
  st_write(., '../geodata/political/political.shp', quiet = T, append = F)

sf::st_read('../geodata/allotments/allotments.shp', quiet = T) %>% 
  dplyr::mutate(Allotment = str_to_title(ALLOT_NAME)) %>% 
  dplyr::select(-ALLOT_NAME) %>% 
  st_write(., '../geodata/allotments/allotments.shp', quiet = T, append = F)

sf::st_read('../geodata/plss/plss.shp', quiet = T) %>% 
  rename(trs = TRS) %>% 
  st_write(., '../geodata/plss/plss.shp', quiet = T, append = F)

sf::st_read('../geodata/pad/pad.shp', quiet = T) %>% 
  sf::st_make_valid() %>% 
  dplyr::filter(sf::st_is_valid(.)) %>% 
  mutate(Unit_Nm = str_replace(Unit_Nm, "National Forest", "NF"),
         Unit_Nm = str_replace(Unit_Nm, "Field Office", "FO"),
         Unit_Nm = str_replace(Unit_Nm, "National Wildlife Refuge", "NWR")) %>% 
  st_write(., '../geodata/pad/pad.shp', quiet = T, append = F)

```
